---
title: "clubSandwich-Stata-functions"
author: "James E. Pustejovsky"
date: "December 12, 2016"
output: html_document
---

# Task 1: clubSandwich versions of reg and areg

Develop a command to fit linear regressions by OLS/WLS, calculate the clubSandwich standard errors, and calculate small-sample t-tests for each coefficient. The command should:

* allow for factor variables via `xi:`.
* have an option to absorb fixed effects, as in the `areg` command.
* work with `pweight`s and `aweight`s.
* _disregard absorbed fixed effects_ when calculating the adjustment matrices, degrees of freedom, etc. 
* save the abjustment matrices and any other required information for calculating F-tests based on the fitted model.

Suggested syntax is as follows:
```{}
reg_sandwich depvar [indepvars] [if] [in] [weight], cluster(varname) [absorb(varname)]
```

If the `absorb` option is present, then the model should be fit as in `areg`. If the option is absent, then the model should be fit as in `reg`. If weights are included, the model should be fit via WLS. The working variance matrix used to calculate the adjustment matrices will depend on which type of weights are used:

* If weights are not used, then the working variance matrix should be an identity matrix.
* If `pweight`s are used, then the working variance matrix should be an identity matix.
* If `aweight`s are used, then the working variance matrix should be diagonal with diagonal entries equal to the inverses of the weights (i.e., we assume that the weights are inverse-variance). 

To verify that the command is correct, replicate the following analysis:

```{r, message = FALSE}
library(haven)
library(dplyr)
library(clubSandwich)
library(plm)

data(MortalityRates)
write_dta(MortalityRates, path = "MortalityRates.dta")

MV_Mortality <- filter(MortalityRates, cause=="Motor Vehicle")

# model specification

specification <- mrate ~ 0 + legal + beertaxa + beerpercap + winepercap + factor(year)
  
# unweighted
ols_pooled <- lm(specification, data = MV_Mortality)
coef_test(ols_pooled, vcov = "CR2", cluster = MV_Mortality$state)

# a-weighted
wls_pooled <- lm(specification, weights = pop, data = MV_Mortality)
vcovCR(wls_pooled, cluster = MV_Mortality$state, type = "CR2", inverse_var = TRUE)[1:4,1:4]
coef_test(wls_pooled, vcov = "CR2", cluster = MV_Mortality$state, inverse_var = TRUE)

# p-weighted
coef_test(wls_pooled, vcov = "CR2", cluster = MV_Mortality$state, inverse_var = FALSE)

```

To check that absorption is working correctly, replicate the following analysis while absorbing the state fixed effects:

```{r, message = FALSE}

# unweighted
ols_within <- plm(update(specification, . ~ . - 0), data = MV_Mortality, effect = "individual", index = c("state","year"))
coef_test(ols_within, vcov = "CR2")

# a-weighted
wls_within <- lm(update(specification, . ~ . + factor(state)), weights = pop, data = MV_Mortality)
coef_test(wls_within, vcov = "CR2", cluster = MV_Mortality$state, inverse_var = TRUE)

# p-weighted
coef_test(wls_within, vcov = "CR2", cluster = MV_Mortality$state, inverse_var = FALSE, ignore_FE = TRUE)

```

# Task 2: clubSandwich F-test

Develop a post-estimation command for testing multiple linear constraints on the regression specification, using the small-sample F-test developed in Pustejovsky & Tipton (2016). The command should follow the same basic syntax as the `test` command:

```{}
test_sandwich <spec> [<spec> ...]
```

where `<spec>` may be a `coeflist` or a set of expressions `exp = exp [= exp ...]`. As with your work on `robumeta`, it may make sense to implement the t-tests in Task 1 using the `test_sandwich` command. 

To verify that the command is correct, replicate the following analysis:
```{r}
constraints <- c(combn(4,2,simplify=FALSE), combn(4,3,simplify = FALSE), list(1:4))

# unweighted, without state effects
Wald_test(ols_pooled, constraints = constraints, 
          vcov = "CR2", cluster = MV_Mortality$state) %>% 
  bind_rows()

# a-weighted, without state effects
Wald_test(wls_pooled, constraints = constraints, 
          vcov = "CR2", cluster = MV_Mortality$state, inverse_var = TRUE) %>% 
  bind_rows()

# p-weighted, without state effects
Wald_test(wls_pooled, constraints = constraints, 
          vcov = "CR2", cluster = MV_Mortality$state, inverse_var = FALSE) %>% 
  bind_rows()

# unweighted, with state effects
Wald_test(ols_within, constraints = constraints, 
          vcov = "CR2") %>% 
  bind_rows()

# a-weighted, with state effects
Wald_test(wls_within, constraints = constraints, 
          vcov = "CR2", cluster = MV_Mortality$state, inverse_var = TRUE) %>% 
  bind_rows()

# p-weighted, with state effects
Wald_test(wls_within, constraints = constraints, 
          vcov = "CR2", cluster = MV_Mortality$state, inverse_var = FALSE, ignore_FE = TRUE) %>% 
  bind_rows()

```

# R session information

```{r}
sessionInfo()
```

